\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Updated Code Appendix
add figures

@@

@@

\appendix
\section{Code}
\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=4in]{B(t).png}
\caption{An example of a zone's population density as a function of travel time from another zone.}
\label{B(t)}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}

\includegraphics[width=4in]{A(t)B(t).png}
\caption{An2 example of a zone's population density as a function of travel time from another zone.}
\label{A(t)B(t)}
\end{center}
\end{figure}

@@

\appendix
\section{Code}
The following contains the code for both our brute force location optimizer, as well as the greedy optimizer. Both functions take a parameter $nambulances$, representing the total number of ambulances we have to allocate across the county.

\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
